Towards a Verified Tableau Prover for Multi-Level-Syllogistics

### 2022-09-12 paper/paper.tex
Continue

Every unsatisfiable formula has a closed tableau so we can determine the satisfiability of a formula \lstinline!$\psi$! by passing the singleton branch \lstinline![$\psi$]! to \lstinline!mlss_proc_branch!. 
Because this is the only context that \lstinline!mlss_proc_branch! is used in, it only encounters branches that result from applying branch expansion rules to a singleton branch.
We call this kind of branches \textit{well-formed} branches and define a predicate for it.
In the definition, the expression \lstinline!&\expandss{b'}{b}&! denotes that \lstinline!b'! is one of the branches that results from applying (potentially zero) expansion rules to \lstinline!b!.
\begin{lstlisting}
definition wf_branch b $\equiv$ $\exists$$\phi$. &\expandss{b}{[$\phi$]}&
\end{lstlisting}
In particular, we will use this notion in \autoref{sec:bound} where derive an upper bound for the cardinality of a well-formed branch.
This is then used in \autoref{sec:correct} to justify the termination of the decision procedure. 
Before we come to that, though, we prove soundness and completeness in Section~\ref{sec:sound} and~\ref{sec:complete}, respectively.
In \autoref{sec:correct}, we also show that both properties easily transfer to the decision procedure which, together with termination, give us total correctness.

@@

theorem mlss_proc_complete:
  fixes $\phi$ :: 'a pset_fm
  assumes $\neg$ mlss_proc $\phi$
  assumes infinite (UNIV :: 'a set)
  shows $\exists$M. M $\models$ $\phi$
\end{lstlisting}

\begin{lstlisting}
lemma mlss_proc_branch_sound:
  assumes wf_branch b
  assumes $\forall$$\psi$ $\in$ set b. M $\models$ $\psi$
  shows $\neg$ mlss_proc_branch b

>>>>

Every unsatisfiable formula has a closed tableau so we can determine the satisfiability of a formula \lstinline!$\psi$! by passing the singleton branch \lstinline![$\psi$]! to \lstinline!mlss_proc_branch!. 
Because this is the only context that \lstinline!mlss_proc_branch! is used in, it only encounters branches that result from applying branch expansion rules to a singleton branch.
We call this kind of branches \textit{well-formed}.
In the definition, the expression \lstinline!&\expandss{b'}{b}&! denotes that \lstinline!b'! is one of the branches that results from applying (potentially zero) expansion rules to \lstinline!b!.
\begin{lstlisting}
definition wf_branch b $\equiv$ $\exists$$\phi$. &\expandss{b}{[$\phi$]}&
\end{lstlisting}
In particular, we will use this notion in \autoref{sec:bound} where derive an upper bound for the cardinality of a well-formed branch.
This is then used in \autoref{sec:correct} to justify the termination of the decision procedure. 
Before we come to that, though, we prove soundness and completeness in Section~\ref{sec:sound} and~\ref{sec:complete}, respectively.
In \autoref{sec:correct}, we also show that both properties easily transfer to the decision procedure which, together with termination, gives us total correctness.

@@

\end{lstlisting}

\begin{lstlisting}
lemma mlss_proc_branch_sound:
  assumes wf_branch b
  assumes $\forall$$\psi$ $\in$ set b. M $\models$ $\psi$
  shows $\neg$ mlss_proc_branch b
\end{lstlisting}

\begin{lstlisting}
theorem mlss_proc_complete:
  fixes $\phi$ :: 'a pset_fm
  assumes $\neg$ mlss_proc $\phi$
  assumes infinite (UNIV :: 'a set)
  shows $\exists$M. M $\models$ $\phi$
